%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage{moderncviconsawesome}
\usepackage{tabularx}
% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page
\moderncvicons{awesome}

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8,top=2cm, bottom=2cm]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\newcommand*\hrefico[2]{%
  \href{#1}{#2}\,\raisebox{-1pt}{\footnotesize\faExternalLink}%
}

% personal data
\name{José}{Villegas}
\title{Resume}                               % optional, remove / comment the line if not wanted
\address{Prenzlauer Berg, Pankow}{Berlin, Germany}{}
%{* September 6th, 1992, Caracas (Venezuela)}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+49~1575~5713499}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{villegasjose.gg@gmail.com}                   % optional, remove / comment the line if not wanted
\homepage{\httplink[jose-villegas.github.io]{jose-villegas.github.io/?utm_source=CV&utm_medium=Curriculum&utm_campaign=Gather&utm_id=Social}}                  % optional, remove / comment the line if not wanted
\extrainfo{\githubsocialsymbol\httplink{github.com/jose-villegas}\maketitlesymbol\linkedinsocialsymbol \httplink{www.linkedin.com/in/villegasjose}}

%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
Game Developer, BA in Computer Science with a specialization in Computer Graphics. My area of expertise includes: gameplay, UI/UX \& graphics programming, breaking down tasks and creating an efficient \& collaborative development pipeline. Motivated and eager to learn from others and share my own experience.

\section{Technical Skills}
\cvitem{Languages}{C\#, C++, C, Shaders, JavaScript, Python, Objective-C, Java, Shell Script, HTML, CSS.}
\cvitem{Tools}{Git, SVN, Jetbrains Rider, Xcode, Jira, Perforce, Azure DevOps, Jenkins, Figma, Firebase, AWS.}
\cvitem{Tech Stack}{Unity3D, Addressables, Zenject, UniRX, UniTask, Unity DOTS, Timeline, SOLID, TDD.}

\section{Languages}
\vspace*{-\baselineskip}
\begin{tabularx}{\textwidth}{@{} XXX}\\
  \cvitemwithcomment{Spanish}{Native.}{} & \cvitemwithcomment{English}{Bilingual.}{} & \cvitemwithcomment{German}{Elementary.}{}
\end{tabularx}
\vspace{0.2cm}

\vspace*{-\baselineskip}
\section{Experience}
\subsection{Professional}
\cventry{Mar. 2020--Jan. 2024 (3 yrs 11 mos)}{Santiago, Chile (Hybrid)}{Lead Game Developer, Game Developer, C\# \& Unity3D}{Globant}{}
{\cvitem{}{
  \begin{itemize}
      \item Collaborated with games from Hasbro's \hrefico{https://www.youtube.com/watch?v=QYcHgdB5_II}{\emph{Power Rangers: Morphin Legends}}, and ABinBev's \hrefico{https://reignoftitans.gg/}{\emph{Reign Of Titans}}
      \item Led a team of developers from ideation to release within 2 years for the game \emph{Power Rangers: Morphin Legends}.
      \item Development of complex battle systems, rendering solutions, CI/CD pipeline, live content (Addressables), MVPs.
      \item Unity SDK development, calibration software and consulting for clients: \hrefico{https://www.bigfishgames.com/us/en/pc-games.html}{\emph{Big Fish}}, \hrefico{https://about.meta.com/}{\emph{Oculus}} and \hrefico{https://www.aristocrat.com/}{\emph{Aristocrat}} 
    \end{itemize}
  }
  % , and solutions for clients such as: Big Fish Games, Aristocrat \& Oculus. My role included: gameplay technical design and development, graphics, scalable game architecture, UI/UX, SDK Integration, analytics, CI build pipeline, live content (Addressables), team planning \& mentoring, optimization, leadership responsibilities and delivery standards.
}
\cventry{Jul. 2017--Mar. 2020 (2 yrs 9 mos)}{Santiago, Chile (On-site)}{Game Developer, C\# \& Unity3D}{Gamaga, Ltd}{}
{\cvitem{}{
  \begin{itemize}
      \item Collaborated with the games: \hrefico{https://play.google.com/store/apps/details?id=com.spilgames.OperateNow2&hl=en}{\emph{Operate Now}}, \hrefico{https://play.google.com/store/apps/details?id=com.gamaga.DecorateProperty&hl=en}{\emph{Holly's Home Design}}, \hrefico{https://play.google.com/store/apps/details?id=com.fdgentertainment.bananakong&hl=en}{\emph{Banana Kong}} and \hrefico{https://www.gamaga.com/red-crimes-hidden-murders}{\emph{Red Crimes}}
      \item Development of features that led to major KPIs growth, from FTUE improvements to late game content.
      \item Learnt LiveOps pipeline, leadership \& mentoring skills, planning and mobile development for iOS \& Android.
      \item Multiple responsibilities: integrating SDKs, analytics, bug-fixing, optimization, rendering and CI/CD solutions.
    \end{itemize}
  }
% Collaborated on projects such as \emph{Operate Now : Hospital} (30M+ downloads), \emph{Holly's Home Design}, \emph{Banana Kong} (100M+ downloads) and \emph{Red Crimes: Hidden Murders}, implementing technical features, integrating new content, live content (AssetBundles), SDK Integration,  bug fixing, optimization, and tools. Increased major KPIs. Learnt leading skills, LiveOps, planning \& mentoring, scalable architecture design, CI build pipeline and delivery standards.
}
%\cventry{May. 2017--Jul. 2017 (3 mos)}{USA-Venezuela}{C, C++ Programmer (Remote)}{NCH Software}{}{Maintaining, improving and adding functionalities over audio and invoice management software.}
\cventry{Nov. 2015--Nov. 2016 (1 yr 2 mos)}{Melbourne, Australia (Remote)}{Junior Game Developer, C\# \& Unity3D}{LearnSafari}{}
{\cvitem{}{
  \begin{itemize}
      \item Collaborated with the game: \hrefico{https://www.learnsafari.com/}{\emph{Learn Safari}} An educational game meant to teach children Spanish lessons.
      \item Development of gameplay mechanics, quest systems, narrative \& cinematics system, graphics and UI/UX logic.
    \end{itemize}
  }
% Development of the game \emph{Learn Safari}. A educational game meant to teach children Spanish through different lessons with multiple interactive mini-games and a narrative story to follow. My first professional role implementing gameplay mechanics, graphics, UX/UI logic, quest systems and mini-games. Learnt many development paradigms.
}
\subsection{Internship}
\cventry{Apr. 2015--Aug. 2015 (6 mos)}{Caracas, Venezuela (On-site)}{Game Development Laboratory Researcher}{UCV, Computer Graphics Center}{Prof. Esmitt Ramírez}{
  \cvitem{}{
    \begin{itemize}
        \item Development \& research on practical material for a game development laboratory using Unity3D within the faculty.
      \end{itemize}
    }
}
\subsection{Vocational}
\cventry{Mar. 2012--Jul. 2012 (6 mos)}{Caracas, Venezuela (On-site)}{Teacher Assistant, Operative Systems}{UCV, Faculty of Sciences}{Prof. Robinson Rivas}
{ \cvitem{}{
  \begin{itemize}
      \item Lectures on the Operative Systems laboratory course using C, Shell Script and Assembly x86 programming.
      \item Tutoring on system calls \& shell commands, usage of threads \& processes, file systems \& parallel programming.
    \end{itemize}
  }
}

\section{Education}
\cventry{2009--2016}{Central University of Venezuela (UCV)}{Licentiate Degree in Computer Science, Faculty of Sciences}{Caracas, Paseo Los Ilustres}{Graduated with Honors}{Specialization: Computer Graphics.}  % arguments 3 to 6 can be left empty
% \cventry{2006--2009}{High School}{Nuestra Madre School}{Caracas, Paseo Los Ilustres}{\textit{High School Graduate}}{}
%\cventry{year--year}{Degree}{Institution}{Street}{\textit{Grade}}{Description}

\section{Master Thesis}
\cvitem{}{\hrefico{https://www.youtube.com/watch?v=e1r5VrDtG7k}{\emph{Voxel Shading and Cone Tracing for Global Illumination}}}
\cvitem{}{Prof. Esmitt Ram\'{i}rez, \textit{Faculty of Sciences, Computer Science Department, Computer Graphics Center}}
\cvitem{}{A real-time dynamic global illumination approach based on cone tracing for emissive, diffuse and specular surfaces utilizing voxel shading and compute shaders. \hrefico{https://ieeexplore.ieee.org/document/7833375}{Per-review paper published for the 2016 XLII Latin American Computing Conference.}}

\section{Conferences \& Game Jams}
{\textit{\textbf{Caracas - Venezuela }}}\cvitem{| Global GameJam 2015, 2016, 2017, 2018}{A game jam global event where you have to make a game in 48 hours. I collaborated on the design of mechanics and development of these games: \hrefico{https://globalgamejam.org/2015/games/kidz-solution}{"Kidz Solution"}, \hrefico{https://globalgamejam.org/2016/games/haunt}{"The Haunt"}, \hrefico{https://globalgamejam.org/2017/games/echo-switch}{"Echo Switch"} and \hrefico{https://globalgamejam.org/2018/games/emission}{"Emission"}}
{\textit{\textbf{Caracas - Venezuela }}}\cvitem{| 5th JOINCIC 2012}{A computer science conference with many talks and courses of different topics on computer science such as web development, game development, robotics, parallel computing, data processing, etc.}
{\textit{\textbf{Caracas - Venezuela }}}\cvitem{| CEIDEC 2012 -  UCV GameDev Contest}{A scientific research and development conference with a broad range of talks from different areas such as math, physics, biology and computer science. Developed the game \hrefico{http://www.elchiguireliterario.com/2012/11/20/resumen-del-ucv-gamedev-contest-2012/}{"Hybris"} using Unity3D along with many teammates on different roles for the GameDev Contest, I worked mostly on artificial intelligence and game mechanics. Hibris is a god game where the player has to save humanity from imminent doom using different powers.}

\section{Hobbies \& Interests}
\cvitem{Gaming}{I also enjoy playing video games as much as working on game development, I mostly game on PC or Consoles, and a few mobile games too. I like to learn the game mechanics, graphics or systems and deconstruct or think how they were implemented. Working on games has in many ways changed my personal experience while playing. Let's get to know our favorite games!}
\cvitem{Cooking \& Food}{I have been home cooking for as far back as I can remember; cooking was a bonding time for me and my mother. I also consider myself a bit of a foodie, always seeking new places to try. I have some classic go-to recipes, and I'm always willing to try new things and share what I know.}
\cvitem{Music \& Instruments}{A significant portion of who I am is shaped by my passion and near obsession with music. I research and collect music from different eras and genres. I've been playing the piano and classical guitar for a few years, and I also know a little bit about music theory.}
\cvitem{Movies}{Movies is something I do enjoy once in a while, maybe not a cinephile but I know a bit. Throughout my life, I have accumulated a substantial collection of films in memory. I occasionally enjoy doing a little research into more unknown titles or cult classics. I'm down to share \& listen to some recommendations.}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
% \bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file


%\clearpage\end{CJK*}                              % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `template.tex'.
